Breareal

### 2022-08-05 indicators/breareal.Rmd
add terra to breareal

```{r, include=FALSE, message=FALSE}
library(knitr)
library(sf)
library(raster) # only needed for creating boundary boxes, which can be done using sf
library(dplyr)
library(lwgeom)
library(tmap)
library(dplyr)
#library(ggplot2)
#library(data.table)
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

```{r, include=FALSE, message=FALSE}
library(knitr)
library(sf)
library(terra)
library(raster) # only needed for creating boundary boxes, which can be done using sf
library(dplyr)
library(lwgeom)
library(tmap)
library(dplyr)
#library(ggplot2)
#library(data.table)
knitr::opts_chunk$set(echo = TRUE)
```
